Lesson 4
========================================================

***

### Scatterplots and Perceived Audience Size
Notes:

***

### Scatterplots
Notes:

```{r Scatterplots}
library(ggplot2)
df <- read.csv("pseudo_facebook.tsv", sep = "\t")
qplot(age, friend_count,data= df)
```

***

#### What are some things that you notice right away?
Response:
Users around 20's has way a lot friends than most of users. 
Vertical bars at the age 69 and 100. Lie about the ages. 
***

### ggplot Syntax
Notes:

```{r ggplot Syntax}
p <- ggplot(aes(x = age, y = friend_count), data = df) 
  p + 
  geom_point() +
  xlim(13, 90)

# summary(df$age)
```

***

### Overplotting
Notes:
Too many points are stacking over each other. For instance, the lower area in the plot. 
It is hard to tell how many points are in each region. 
Use alpha parameter.

```{r Overplotting: set alpha to 1/ 20. Which means every 20 points in the data is equivalent to one point in the plot. Also, swap out the point with jitter, because age is a continuous value. In the point plot, it becomes an integer. Use jitter to add some noise.}
p_jitter <- ggplot(aes(x = age, y = friend_count), data = df) + 
  geom_jitter(alpha = 1 / 20) +
  xlim(13, 90)
p_jitter

```

#### What do you notice in the plot?
Response:
For the younger users, the bulk of friend count is below 1000. Since using alpha = 1/20, every 20 points will make a black circle. The count above 1000 is transparent. 
***

### Coord_trans()
Notes:

```{r Coord_trans()}
p_trans <-  ggplot(aes(x = age, y = friend_count), data = df) + 
  geom_point(alpha = 1 / 20) +
  xlim(13, 90) + 
  coord_trans(y = "sqrt")
p_trans
```


#### Look up the documentation for coord_trans() and add a layer to the plot that transforms friend_count using the square root function. Create your plot!

```{r To add noise into the plot. Use jitter}
p_jitter_trans <-  ggplot(aes(x = age, y = friend_count), data = df) + 
  geom_point(alpha = 1 / 20, position = position_jitter(h = 0)) +
  xlim(13, 90) + 
  coord_trans(y = "sqrt")
p_jitter_trans

```

#### What do you notice?

***

### Alpha and Jitter
Notes:
Explore the relationship between friendships_initiated vs age
```{r Alpha and Jitter}
ggplot(data = df, aes(x = age, y = friendships_initiated)) + 
  geom_jitter(alpha = 1/10, position= position_jitter(h = 0), colour = "navyblue") +
  coord_trans(y = "sqrt")
```

***

### Overplotting and Domain Knowledge
Notes:

***

### Conditional Means
Notes:

```{r Conditional Means}
library(dplyr)
age_groups <- group_by(df, age)
df.fc_by_age <- summarise(age_groups,
                          friend_count_mean = mean(friend_count), 
                          friend_count_median = median (friend_count), 
                          n = n())

df.fc_by_age <- arrange(df.fc_by_age )
head(df.fc_by_age)
```

### Conditional Means Alternative Code
Notes:

```{r Conditional Means. Use %.% chain functions}
library(dplyr)
df.fc_by_age <- df %.% 
  group_by(age) %.%
  summarise(friend_count_mean = mean(friend_count),
            friend_count_median = median(friend_count), 
            n = n()) %.%
  arrange(age)
        
head(df.fc_by_age)
```

Create your plot!

```{r Conditional Means Plot}
ggplot(data = df.fc_by_age, aes(x = age, y = friend_count_mean)) +
  geom_line() 
```

***

### Overlaying Summaries with Raw Data
Notes:

```{r Overlaying Summaries with Raw Data}
ggplot(data = df, aes(x = age, y = friendships_initiated)) + 
  geom_jitter(alpha = 1/10, position= position_jitter(h = 0), colour = "navyblue") +
  coord_trans(y = "sqrt") + 
  xlim(13, 90) +
  geom_line(stat = "summary", fun.y = mean) +
  geom_line(stat = "summary", fun.y = quantile, probs = 0.1, linetype =2, color = "orange") +
geom_line(stat = "summary", fun.y = quantile, probs = 0.5, linetype =3, color = "red") +
  geom_line(stat = "summary", fun.y = quantile, probs = 0.9, linetype =4, color = "pink")
```

```{r Overlaying Summaries with Raw Data. Use coord_cartesian}
ggplot(data = df, aes(x = age, y = friendships_initiated)) + 
  geom_jitter(alpha = 1/10, position= position_jitter(h = 0), colour = "navyblue") +
  coord_cartesian(xlim = c(13, 70), ylim = c(0, 1000)) + 
  geom_line(stat = "summary", fun.y = mean) +
  geom_line(stat = "summary", fun.y = quantile, probs = 0.1, linetype =2, color = "orange") +
geom_line(stat = "summary", fun.y = quantile, probs = 0.5, linetype =3, color = "red") +
  geom_line(stat = "summary", fun.y = quantile, probs = 0.9, linetype =4, color = "purple")
```

#### What are some of your observations of the plot?
Response:

***

### Moira: Histogram Summary and Scatterplot
See the Instructor Notes of this video to download Moira's paper on perceived audience size and to see the final plot.

Notes:

***

### Correlation
Notes:

```{r Correlation}
cor.test(df$age, df$friend_count)
```

```{r Correlation Alternative}
with(df, cor.test(df$age, df$friend_count))
```


Look up the documentation for the cor.test function.

What's the correlation between age and friend count? Round to three decimal places.
Response:

***

### Correlation on Subsets
Notes:

```{r Correlation on Subsets}
with(    subset(df,  age <= 70)             , cor.test(age, friend_count))
```

***

### Correlation Methods
Notes:

***

## Create Scatterplots
Notes:

```{r}
ggplot(data = df, aes(x = www_likes_received, y =likes_received )) + 
  geom_point() 
```

***

### Strong Correlations
Notes:

```{r Strong Correlations. Use quantile to limit the outliers}
ggplot(data = df, aes(x = www_likes_received, y =likes_received )) + 
  geom_point() + 
  coord_cartesian(xlim = c(0, quantile(df$www_likes_received, 0.95)), ylim = c(0, quantile(df$likes_received, 0.95)))+
  geom_smooth(method = "lm", color = "red")
```

What's the correlation betwen the two variables? Include the top 5% of values for the variable in the calculation and round to 3 decimal places.

```{r Correlation Calcuation}
cor.test(df$www_likes_received, df$likes_received)

```

Response:

***

### Moira on Correlation
Notes:
Helps to determine which variables are related.
***

### More Caution with Correlation
Notes:

```{r More Caution With Correlation}
#install.packages('alr3')
library(alr3)
data(Mitchell)
```

Create your plot!

```{r Temp vs Month}
ggplot(data = Mitchell, aes(x = Month, y = Temp)) + 
  geom_point() 

```

***

### Noisy Scatterplots
a. Take a guess for the correlation coefficient for the scatterplot.

b. What is the actual correlation of the two variables?
(Round to the thousandths place)

```{r Noisy Scatterplots}
cor.test(Mitchell$Month, Mitchell$Temp)
```

***

### Making Sense of Data
Notes:

```{r Making Sense of Data}
ggplot(data = Mitchell, aes(x = Month, y = Temp)) + 
  geom_point() + 
  scale_x_discrete(breaks = seq(0, 204, 12)) 
```

***

### A New Perspective

What do you notice?
Response:

Watch the solution video and check out the Instructor Notes!
Notes:
Proportion of y and x affects recognising the pattern.
***

### Understanding Noise: Age to Age Months
Notes:

```{r Understanding Noise: Age to Age Months}
ggplot(data = df.fc_by_age, aes(x = age, y  = friend_count_mean)) + geom_line()

```

***

### Age with Months Means

```{r Age with Months Means}
df$age_with_month <-df$age + 1 - df$dob_month / 12
age_with_month_group <- group_by(df, age_with_month)

```

Programming Assignment
```{r Programming Assignment}
df.fc_by_age_with_month <- summarise(age_with_month_group, 
                                    fc_mean = mean(friend_count)) 
head(df.fc_by_age_with_month)

ggplot(data = df.fc_by_age_with_month, aes(x = age_with_month, y = fc_mean )) + 
  geom_line() + 
  scale_x_continuous(limits = c(0, 71)) 

```

***

### Noise in Conditional Means

```{r Noise in Conditional Means}
ggplot(data = df.fc_by_age_with_month, aes(x = age_with_month, y = fc_mean )) + 
  geom_line() + 
  scale_x_continuous(limits = c(0, 71)) 
```

***

### Smoothing Conditional Means
Notes:

```{r Smoothing Conditional Means}
library(gridExtra)
p1 <- ggplot(data = subset(df.fc_by_age, age < 71), aes(x= age, y = friend_count_mean)) + geom_line()

p2 <- ggplot(data = subset(df.fc_by_age_with_month,age_with_month < 71), aes(x = age_with_month, y = fc_mean ))+ 
  geom_line() 

p3 <- ggplot(data = subset(df, age < 71), aes(x = round(age/ 5) * 5, y = friend_count )) + 
  geom_line(stat = "summary" , fun.y = mean) 

grid.arrange(p1, p2, p3, ncol=1)
```

***

### Which Plot to Choose?
Notes:

***

### Analyzing Two Variables
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

