Lesson 5
========================================================

### Multivariate Data
Notes:

***

### Moira Perceived Audience Size Colored by Age
Notes:

***
```{r Read data}
pf = read.delim("pseudo_facebook.tsv")
library(ggplot2)
```

### Third Qualitative Variable
Notes:

```{r Third Qualitative Variable}

ggplot(aes(x = gender, y = age),
       data = subset(pf, !is.na(gender))) + geom_boxplot() + 
  stat_summary(fun.y = mean, geom = "point", shape= 3)

ggplot(aes(x = age, y = friend_count),
       data = subset(pf, !is.na(gender)))  +
  geom_line(aes(color = gender), stat = "summary", fun.y = "median" )
```

***

### Plotting Conditional Summaries
Notes:

```{r Plotting Conditional Summaries}
suppressMessages(library(dplyr))
age_gender_group <- group_by(subset(pf, !is.na(gender)), age, gender)
pf.fc_by_age_gender <- ungroup(summarise(age_gender_group, 
                                 mean_friend_count = mean(friend_count),
                                  median_friend_count = median(friend_count),
                                 n = n()))
pf.fc_by_age_gender <- arrange(pf.fc_by_age_gender, age)
head(pf.fc_by_age_gender)
```

```{r}
ggplot(data = pf.fc_by_age_gender, aes(x = age, y = median_friend_count)) + geom_line(aes(color = gender)) 
```


***

### Thinking in Ratios
Notes:

***

### Wide and Long Format
Notes:

***

### Reshaping Data
Notes:It’s important to use quotes around the variable name that is assigned to value.var. 

```{r}
#install.packages('reshape2')
library(reshape2)

pf.fc_by_age_gender.wide <- dcast(pf.fc_by_age_gender, 
                                  age ~ gender,
                                  value.var = "median_friend_count")
```


***

### Ratio Plot
Notes:

```{r Ratio Plot}
pf.fc_by_age_gender.wide$ratio <- pf.fc_by_age_gender.wide$female / pf.fc_by_age_gender.wide$male
ggplot(data = pf.fc_by_age_gender.wide, aes(x = age, y = ratio)) + 
  geom_line() +
  geom_hline(aes(yintercept = 1, color = "red", alpha = 0.3)) 

```

***

### Third Quantitative Variable
Notes: Create a variable called year_joined in the pf data frame using the variable tenure and 2014 as the reference year.

The variable year joined should contain the year that a user joined facebook.


```{r Third Quantitative Variable}
pf$year_joined <- floor(2014 - pf$tenure / 365)

```

***

### Cut a Variable
Notes:
cut: break up a continuous variable such as age into a categorical variable.

Create a new variable in the data frame called "year_joined.bucket" by using the cut function on the variable year_joined.

# You need to create the following buckets for the
# new variable, year_joined.bucket

#        (2004, 2009]
#        (2009, 2011]
#        (2011, 2012]
#        (2012, 2014]

```{r Cut a Variable}
pf$year_joined.bucket <- cut(pf$year_joined, breaks = c(2004,2009, 2011, 2012, 2014))
```

***

### Plotting it All Together
Notes:
# Create a line graph of friend_count vs. age
# so that each year_joined.bucket is a line
# tracking the median user friend_count across
# age. This means you should have four different
# lines on your plot.
```{r Plotting it All Together}
p1 <- ggplot(data = subset(pf, !is.na(year_joined.bucket)), aes(x = age, y = friend_count)) +
   geom_line(aes(color = year_joined.bucket), stat = "summary", fun.y = median)
```

***

### Plot the Grand Mean
Notes:

```{r Plot the Grand Mean}
p1 + geom_line(stat = "summary", fun.y = mean, linetype =3)

```

***

### Friending Rate
Notes:

```{r Friending Rate}
pf.tenure_more_than_one_day <- subset(pf, tenure >= 1)
pf.tenure_more_than_one_day$friend_rate <- pf.tenure_more_than_one_day$friend_count / pf.tenure_more_than_one_day$tenure
summary(pf.tenure_more_than_one_day$friend_rate)
```

***

### Friendships Initiated
Notes:

What is the median friend rate?

What is the maximum friend rate?
# Create a line graph of mean of friendships_initiated per day (of tenure)
# vs. tenure colored by year_joined.bucket.

# You need to make use of the variables tenure,
# friendships_initiated, and year_joined.bucket.

```{r Friendships Initiated}

pf.tenure_more_than_one_day$friendships_initiated_rate <- pf.tenure_more_than_one_day$friendships_initiated / pf.tenure_more_than_one_day$tenure 

ggplot(data = pf.tenure_more_than_one_day, aes(x = tenure, y =friendships_initiated_rate ) ) +
  geom_line(aes(color = year_joined.bucket), stat = "summary", fun.y = mean)
```


Notes: Too much noise in the plot because the tenure has all possible value. To sooth this out, change the bin width of x axis. 

***

### Bias-Variance Tradeoff Revisited
Notes:

```{r Bias-Variance Tradeoff Revisited}

ggplot(aes(x = tenure, y = friendships_initiated / tenure),
       data = subset(pf, tenure >= 1)) +
  geom_line(aes(color = year_joined.bucket),
            stat = 'summary',
            fun.y = mean)

ggplot(aes(x = 7 * round(tenure / 7), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

ggplot(aes(x = 30 * round(tenure / 30), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

ggplot(aes(x = 90 * round(tenure / 90), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)


```

# Instead of geom_line(), use geom_smooth() to add a smoother to the plot.
# You can use the defaults for geom_smooth() but do color the line
# by year_joined.bucket

```{r}

ggplot(aes(x = tenure, y = friendships_initiated / tenure),
       data = subset(pf, tenure >= 1)) +
  geom_smooth(aes(color = year_joined.bucket))

```

***

### Sean's NFL Fan Sentiment Study
Notes:

***

### Introducing the Yogurt Data Set
Notes:
```{r}
yo <- read.csv("yogurt.csv")
```

***


### Histograms Revisited
Notes:

```{r Histograms Revisited}
yo$id <- as.factor(yo$id)
str(yo)
ggplot(data = yo, aes(price)) + geom_histogram(binwidth = 10)
```

***

### Number of Purchases
Notes:

```{r Number of Purchases}
yo <- transform(yo, all.purchases = strawberry + blueberry + pina.colada + plain + mixed.berry)
```

***

### Prices over Time
Notes:
# Create a scatterplot of price vs time.
```{r Prices over Time}
ggplot(data = yo, aes(x = time, y = price)) + 
  geom_point()
```

***

### Sampling Observations
Notes:

***

### Looking at Samples of Households

```{r Looking at Sample of Households}
set.seed(328)
sample.ids <- sample(levels(yo$id), 16)

ggplot(data = subset(yo, id %in% sample.ids), aes(x = time, y = price)) + 
  facet_wrap(~id) + 
  geom_line() + 
  geom_point(aes(size = all.purchases), pch = 1) 
  
```

***

### The Limits of Cross Sectional Data
Notes:

***

### Many Variables
Notes:

***

### Scatterplot Matrix
Notes:

***
```{r}
#install.packages("GGally")
library(GGally)
theme_set(theme_minimal(20))

set.seed(1836)
pf.subset <- pf[, c(2:15)]
ggpairs(pf.subset[sample.int(nrow(pf_subset), 1000), ])
```


### Even More Variables
Notes:

***

### Heat Maps
Notes:

```{r}
nci <- read.table("nci.tsv")
colnames(nci) <- c(1:64)
```

```{r}
library(reshape2)
nci.long.samp <- melt(as.matrix(nci[1:200,]))
names(nci.long.samp) <- c("gene", "case", "value")
head(nci.long.samp)

ggplot(aes(y = gene, x = case, fill = value),
  data = nci.long.samp) +
  geom_tile() +
  scale_fill_gradientn(colours = colorRampPalette(c("blue", "red"))(100))
```


***

### Analyzing Three of More Variables
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

