Lesson 3
========================================================

***

### What to Do First?
Notes:

***

### Pseudo-Facebook User Data
Notes:

```{r Pseudo-Facebook User Data}
pf = read.delim("pseudo_facebook.tsv")
names(pf)
```

***

### Histogram of Users' Birthdays
Notes:

```{r Histogram of Users\' Birthdays}
#install.packages('ggplot2')
library(ggplot2)
qplot(x = dob_day, data = pf) +
  scale_x_discrete(breaks = 1:31) +
  facet_wrap(~dob_month, ncol = 3)
```

***

#### What are some things that you notice about this histogram?
Response:

***

### Moira's Investigation
Notes:

***

### Estimating Your Audience Size
Notes:

***

#### Think about a time when you posted a specific message or shared a photo on Facebook. What was it?
Response:

#### How many of your friends do you think saw that post?
Response:

#### Think about what percent of your friends on Facebook see any posts or comments that you make in a month. What percent do you think that is?
Response:

***

### Perceived Audience Size
Notes:

***
### Faceting
Notes:

```{r Faceting}

```

#### Let’s take another look at our plot. What stands out to you here?
Response:

***

### Be Skeptical - Outliers and Anomalies
Notes:

***

### Moira's Outlier
Notes:
#### Which case do you think applies to Moira’s outlier?
Response:

***

### Friend Count
Notes:

#### What code would you enter to create a histogram of friend counts?

```{r Friend Count}
qplot(x = friend_count, data = subset(pf, !is.na(gender)), binwidth = 25) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50)) +
  facet_wrap(~gender)
```

#### How is this plot similar to Moira's first plot?
Response:
long tail
***

### Limiting the Axes
Notes:

```{r Limiting the Axes}

```

### Exploring with Bin Width
Notes:

***

### Adjusting the Bin Width
Notes:

### Faceting Friend Count
```{r Faceting Friend Count}
# What code would you add to create a facet the histogram by gender?
# Add it to the code below.
qplot(x = friend_count, data = pf, binwidth = 10) +
  scale_x_continuous(limits = c(0, 1000),
                     breaks = seq(0, 1000, 50))
```

***

### Omitting NA Values
Notes:

```{r Omitting NA Values}

```

***

### Statistics 'by' Gender
Notes:

```{r Statistics \'by\' Gender}
by(pf$friend_count, pf$gender, summary)
```

#### Who on average has more friends: men or women?
Response: women

#### What's the difference between the median friend count for women and men?
Response: 22

#### Why would the median be a better measure than the mean?
Response:
more robust statistic. A few with high values drag the mean upwards, which is not necessarily 
represent 

***

### Tenure
Notes:

```{r Tenure}
ggplot(aes(x = tenure), data = pf) + 
   geom_histogram(binwidth = 30, color = 'black', fill = '#099DD9')
```

***

#### How would you create a histogram of tenure by year?

```{r Tenure Histogram by Year}
qplot(x = tenure / 365, data = pf, binwidth = 0.5, color = I("black"), fill = I("orange")) + 
  scale_x_continuous(seq(1, 7, 1), limits = c(0, 7))
```

***

### Labeling Plots
Notes:

```{r Labeling Plots}
qplot(x = tenure / 365, data = pf,  
      xlab = "Number of yrs on FB", ylab = "Number of users",
      binwidth = 0.5, color = I("black"), fill = I("orange") ) + 
  scale_x_continuous(seq(1, 7, 1), limits = c(0, 7))

```

***

### User Ages
Notes:

```{r User Ages}
qplot(x = age, data = pf,
      xlab = "Age", ylab = "Number of users",binwidth = 1, color = I("black"), fill = I("green")) +
  scale_x_continuous(seq(13, 113, 1))

```

#### What do you notice?
Response:

***

### The Spread of Memes
Notes:

***

### Lada's Money Bag Meme
Notes:

***

### Transforming Data
Notes:

***

### Add a Scaling Layer
Notes:

```{r Add a Scaling Layer}
#install.packages("gridExtra")
library("gridExtra")
p1 = qplot(x = friend_count, data = pf, main = "Original")
p2 = qplot(x = log(friend_count + 1), data = pf, main = "Log base 10") 
p3 = qplot(x = sqrt(friend_count), data = pf, main = "SQRT") 
grid.arrange(p1, p2, p3, ncol = 1)
```

### ggplot syntax
```{r}
library("gridExtra") 
p1 = ggplot(pf, aes(x = friend_count)) + geom_histogram()
p2 = p1 + scale_x_log10()
p3 = p1 + scale_x_sqrt()
grid.arrange(p1, p2, p3, ncol = 1)

```


***


### Frequency Polygons

```{r Frequency Polygons}
qplot(x = www_likes, 
      data = subset(pf, !is.na(gender)), geom = "freqpoly", color = gender) +
  scale_x_continuous()+ 
  scale_x_log10()

```

***

### Likes on the Web
Notes:

```{r Likes on the Web}

```


***

### Box Plots
Notes:

```{r Box Plots}

```

#### Adjust the code to focus on users who have friend counts between 0 and 1000.

```{r}

```

***

### Box Plots, Quartiles, and Friendships
Notes:


```{r Box Plots, Quartiles, and Friendships}
qplot(x = gender, y = friend_count, data = subset(pf, !is.na(gender)), ,geom = "boxplot", ylim = c(0, 1000))     

```

#### On average, who initiated more friendships in our sample: men or women?
Response:
#### Write about some ways that you can verify your answer.
Response:
```{r Friend Requests by Gender}

```

Response:

***

### Getting Logical
Notes:

```{r Getting Logical}

```

Response:

***

### Analyzing One Variable
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!